\chapter{SUPPORTING LITERATURE}

\section{Overview}
The development of the Shopify application relies on several established technologies and architectures in modern web development. The following literature reviews the core concepts and frameworks that formed the foundation of this project.

\section{Modern Web Architectures}
Historically, e-commerce platforms relied on monolithic structures where the server rendered every page. The shift toward Single Page Applications (SPAs) has significantly improved user experience by reducing page load times and providing dynamic, fluid interfaces. Frameworks like React have become industry standards for building such interfaces due to their component-based design and efficient virtual DOM.

\section{The Laravel and React Ecosystem}
Laravel is widely recognized as one of the most robust PHP frameworks, favored for its elegant syntax and comprehensive ecosystem covering authentication, routing, and ORM. Inertia.js acts as the critical glue in this architecture, allowing developers to build classic server-driven web applications while utilizing a modern frontend framework like React, without the complexity of managing a separate API layer.

\section{AI in E-Commerce}
The integration of Machine Learning and embeddings into e-commerce is rapidly evolving. By utilizing vector embeddings to represent product descriptions semantically, platforms can offer highly accurate "similar product" recommendations, moving beyond simple keyword matching and creating a more intuitive shopping experience.
